\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-10-04 bare_conf.tex
removed bibliography duplicate \cite{Poggi}.
some text modification.

The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding vision processing algorithms.

@@

External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and other algorithms, and transmits feedback signal back to the smartphone device for presenting to the user via the above described interface.

@@

Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs. The end users highlighted that a simplistic solution for navigating is lacking. 
%They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
Major focus was put on a easy to use and minimalistic tool, which can be trusted. Object detection, and direction and approximate distance to obstacle were highlighted as major requirements. To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating. Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive. Another important functionality required by end users was navigation aid.

@@

\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning. 2016 IEEE Symposium on Computers and Communication (ISCC), 2016

>>>>

The cornerstones of the proposed solution are its inferface and external server, capable running computationally demanding modern image processing algorithms.

@@

External server processes received visual data according to user request with computer vision algorithms: faster RCNN object detector \cite{Ren}, trained to detect important objects, CNN-RNN-based scene description \cite{Liu}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, among others. After completing an analysis this server transmits feedback signal back to the smartphone device for presenting it to the user via the above described interface.

@@

Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs. For example, the end users highlighted that a simplistic solution for navigating is lacking. 
%They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. 
Major focus was put on a easy to use and minimalistic tool, which can be trusted. Reliable object detection, direction and approximate distance to an obstacle were highlighted as major requirements. To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating. Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.

@@

%\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning. 2016 IEEE Symposium on Computers and Communication (ISCC), 2016
